Response to referees: Multi-target detection with application to cryo-electron microscopy

### 2019-06-03 InverseProblemsV2/reponse.tex
With Amit's comments

\noindent \textbf{Response:} Section 4.4 discusses the application of our approach to 2-D images. In this section, we underscore the importance of the knowledge of the exact support for phase retrieval (recovery from second-order autocorrelation) as was shown in [9]. 
We revised a couple of sentences in this section for the sake of clarity. 
If exact support knowledge is not available, our proposed solution is to consider the third-order autocorrelation.
To demonstrate it, in the revised manuscript, we changed Experiment 1. Now, half of the first signal in Figure 1 is zero, which allows us to simulate the situation in which the support of the signal is overestimated. Our algorithm still recovers the signal accurately. \\

@@

\noindent \textbf{Response:} The number of numbers we compute (as autocorrelations) is a growing function of the signal length $L$. Hence, we expect that, as $L$ grows, we should be able to estimate more and more distinct signals in the heterogeneous case. The experiment reported in Figure 2 illustrates how $K$ (the number of signals we can estimate simultaneously) grows as a function of $L$. Since to do the actual recovery we need to solve a non-convex optimization problem, this experiment is setup so that we can distinguish between the effects of statistical and computational difficulties.

>>>>

\noindent \textbf{Response:} Section 4.4 discusses the application of our approach to 2-D images. For Einstein's image used in the manuscript, the boundary of the second-order autocorrelation  can be identified easily if the second-order autocorrelation is known precisely (that is, $N\to\infty$); see Figure~\ref{fig:XC} (in this report). 
Since the image is square, it implies the support of the image itself. 
In Section 4.4, we underscore the importance of the knowledge of the exact support for phase retrieval (recovery from second-order autocorrelation) as was shown in [9]. 
We revised a couple of sentences in this section for the sake of clarity.

If exact support knowledge is not available, our proposed solution is to consider the third-order autocorrelation.
To demonstrate it, in the revised manuscript, we changed Experiment 1. Now, half of the first signal in Figure 1 is zero, which allows us to simulate the situation in which the support of the signal is overestimated. Our algorithm still recovers the signal accurately. \\

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.3]{Xcorr}
	\caption{	\label{fig:XC} The second-order autocorrelation of Einstein's image used in the paper (padded by zeros).}
\end{figure}

@@

\noindent \textbf{Response:} The number of autocorrelation entries we compute increases with the signal length $L$. Hence, we expect that, as $L$ grows, we should be able to estimate more and more distinct signals in the heterogeneous case. The experiment reported in Figure 2 illustrates how $K$ (the number of signals we can estimate simultaneously) grows as a function of $L$. Since to do the actual recovery we need to solve a non-convex optimization problem, this experiment is setup so that we can distinguish between the effects of statistical and computational difficulties.
